### 2015-02-20 paper_40_mpi.tex
working on schedule

                In order to calculate the schedule score, certain dates
                need to be present. Table \ref{tab:scheduledata} outlines
                the necessary data for schedules.  One date is considered
                optional as it is not used in the MPI calculation, but it
                is an important date that could be useful for future
                enhancements.

@@

            \paragraph{SCHEDULE FORMULA}

>>>>

                In order to calculate the schedule score, certain dates
                need to be present. Table \ref{tab:scheduledata} outlines
                the necessary data for schedules.  One date is considered
                optional as it is not used in the MPI calculation, but it
                is an important date that could be useful for future
                enhancements to MPI.

@@

            \paragraph{SCHEDULE FORMULA}
                Schedule has a clear date for finishing on-time, however
                there are not clear bounds as to how early or late a project
                can be delivered.  Thus, the formula for schedule is more involved
                than availability or satisfaction.  It requires some analysis
                of the historical data.  The first step of the formula is
                determining how often projects are early or late, and by how
                much a project is early or late.  This can be accomplished
                by looking at the distribution of the data.  Specifically,
                look at what percentage of the entire project duration the
                schedule was missed.
